\section{Succinctness}
 As background knowledge and in order to show the final contribution of the presented construction we will now refer to the succinctness of the produced proofs. We will explain the major shortcomings of superblock NIPoPoWs and an estimation for the proofs' length in average case scenarios. The reader should refer to~\cite{nipopows} for a detailed analysis. The content of this section is also mostly borrowed by~\cite{nipopows}.
 
 The basic weakness of the superblock NIPoPow construction results from the importance of the rare ``lucky'' blocks in the chain and the suppression attacks that the adversary can perform on them, as described in a previous section. In essence, the adversary could perform such an attack on a target level $\mu$ rather easy, since $\mu$-superblock appear rarely in the chain and the adversary can suppress them with only one or two blocks of any lower level. Thus, by generating less lucky blocks the adversary has the chance to abort a very lucky honestly generated block.

 Therefore, full succinctness in the standard honest majority model is impossible to prove for superblock NIPoPoWs. Recall that by reducing superquality through suppression attacks for a sufficiently low level $\mu$ the adversary can cause the honest prover to digress in their proofs from high level superchains down to low-level superchains, causing a linear proofs to be produced. For instance, if superquality is harmed at $\mu = 3$, the prover will need to digress down to level $\mu = 2$ and include the whole 2-superchain, which will be of size $\lvert \chain \rvert /2$ in expectation.

 The following theorem gives the succinctness estimation for the particular ``optimistic'' case where the adversary does not use their (minority) computational power or network power.

 \begin{theorem}[Optimistic succinctness]
     If all players are honest and the network scheduling is random, superblock NIPoPoWs produced by honest provers are succinct  with the number of blocks bounded by $4mlog(\lvert \chain \rvert)$, with overwhelming probability in $m$.
\end{theorem}